Estimating the Financial Impact of Wildfire Smoke on US National parks

### 2020-06-01 Markdown Documents/Manuscript.Rmd
testing.
fixed x axis labels on fee revenue predictions vs observed plot. They were off by an order of magnitude

Alex to complete this section

@@

We can apply these visitation estimates to the fee data/predictions also.
```{r echo=FALSE, cache=TRUE, warning=FALSE, message=FALSE, fig.height = 8, fig.width = 13}
financialData<-merge(dat[,c(2,5)],financialData,by="UnitCode")
financialData%>%filter(UnitCode %in% fitsig$Par)%>%group_by(ParkName)%>%
  summarise(sumincome=sum(incomeObserved),sumincomePred=sum(incomePred))%>%ungroup()%>%
  mutate(diff=sumincomePred-sumincome)%>%
  ggplot(., 
         aes(y = reorder(ParkName,diff),
             x = sumincome,
             xend = sumincomePred)) +  
  ggalt::geom_dumbbell(size = 1.2,
                       size_x = 5, 
                       size_xend = 5,
                       colour = "darkgrey", 
                       colour_x = "black", 
                       colour_xend = "#41ab5d",dot_guide = T,dot_guide_size = NULL,dot_guide_colour = "lightgrey")+
  geom_rect( aes(xmin=100500000000, xmax=109500000000, ymin=-Inf, ymax=Inf), fill="grey") +
  geom_text( aes(label=paste0("-",round((diff/sumincome)*100,digits=1), "%"), y=ParkName, x=105000000000), fontface=2, size=4)+
  annotate("text", x = 105000000000, y = "Glacier NP", label = "Difference",vjust=-1.5,fontface=2)+
  scale_x_continuous( labels = scales::dollar_format(prefix = "$")) +
  annotate("text", x = 62000000000, y = "Yosemite NP", label = "Observed fee revenue",vjust=-1,hjust=1,fontface=2)+
  annotate("text", x = 80000000000, y = "Yosemite NP", label = "Predicted fee revenue no smoke",vjust=-1,color="#41ab5d",fontface=2)+
  labs(title = "Total Lost Revenue",
       subtitle = "1980 to 2018",
       x = "Total Visitor Revenue 1980 to 2018",
       y = "")+theme_classic()+mytheme+theme(plot.subtitle = element_text(face = "bold"))

>>>>

Will start this weekend.

@@

We can apply these visitation estimates to the fee data/predictions also.
```{r echo=FALSE, cache=TRUE, warning=FALSE, message=FALSE, fig.height = 8, fig.width = 13}
financialData%>%filter(UnitCode %in% fitsig$Par)%>%group_by(Park)%>%
  summarise(sumincome=sum(incomeObserved),sumincomePred=sum(incomePred))%>%ungroup()%>%
  mutate(diff=sumincomePred-sumincome)%>%
  ggplot(., 
         aes(y = reorder(Park,diff),
             x = sumincome,
             xend = sumincomePred)) +  
  ggalt::geom_dumbbell(size = 1.2,
                       size_x = 5, 
                       size_xend = 5,
                       colour = "darkgrey", 
                       colour_x = "black", 
                       colour_xend = "#41ab5d",dot_guide = T,dot_guide_size = NULL,dot_guide_colour = "lightgrey")+
  geom_rect( aes(xmin=860000000, xmax=940000000, ymin=-Inf, ymax=Inf), fill="grey") +
  geom_text( aes(label=paste0("-",round((diff/sumincome)*100,digits=1), "%"), y=Park, x=900000000), fontface=2, size=4)+
  annotate("text", x = 900000000, y = "Glacier NP", label = "Difference",vjust=-1.5,fontface=2)+
  scale_x_continuous( labels = scales::dollar_format(prefix = "$")) +
  annotate("text", x = 453357090, y = "Yosemite NP", label = "Observed fee revenue",vjust=-1,fontface=2)+
  annotate("text", x = 682294835, y = "Yosemite NP", label = "Predicted fee revenue no smoke",vjust=-1,color="#41ab5d",fontface=2)+
  labs(title = "Total Lost Revenue",
       subtitle = "1980 to 2018",
       x = "Total Visitor Revenue 1980 to 2018",
       y = "")+theme_classic()+mytheme+theme(plot.subtitle = element_text(face = "bold"))
```
